What do incoming university students believe about open science practices in

### 2021-10-29 analysis/Manuscript.Rmd
add credit & update r refs

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
- name: Jennifer L. Beaudry
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: jbeaudry@swin.edu.au
  role: null
- name: Michael C. Philipp
  affiliation: '2'
  role: null
- name: Matt N. Williams
  affiliation: '2'
  role: null
- name: Emily Kothe
  affiliation: '3'
  role: null
shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
authornote: |
  1 Flinders University, Australia
  2 Massey University, New Zealand
  3 Deakin University, Australia
abstract: |
 BACKGROUND: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to the students’ existing understandings.
 OBJECTIVE: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in spsychology.
 METHOD: International online survey with participants who were about to start their first course in psychology at a university (N = 239) .
 RESULTS: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices. When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%. Only 18% of participants had heard of the term "replication crisis".
 CONCLUSION: Despite relatively significant media attention on the replication crisis, few incoming psychology students are familiar with the term. Incoming students nevertheless appear to be sympathetic toward most open science practices, although they may overestimate the prevalence of these practices in psychology.
 TEACHING IMPLICATIONS: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.

keywords: open science, psychology, teaching, reproducibility, replication
wordcount:
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: yes
draft: no
documentclass: apa6
classoption: man
affiliation:
- id: '1'
  institution: Swinburne University of Technology
- id: '2'
  institution: Massey University
- id: '3'
  institution: Deakin University, Geelong, Australia, Misinformation Lab, School of Psychology
editor_options: 
  chunk_output_type: console
csl               : "apa.csl" 
---

@@

<!-- I've only partially entered authorship deets for the moment and set it to mask authorship info when knitting. JB: We'll need to discuss authorship order. I would 
like to use CREDIT for our contributions. 
It's set to default to knit to .docx, but can also knit to pdf (if you have a tex distro installed)
The pdf looks nicer and might be good for a preprint but .docx probably easiest to use for journal submissions. 
JB: Yes, that makes sense.

To knit to RMarkdown you will probably need the papaja package installed, and to knit to .pdf you will need a tex distro (e.g., TinyTex).
However, it is possible to run all the R code (without knitting to .docx or .pdf) by clicking Run > Run All Chunks Below.
This could be useful in future for readers interested in reproducing results but who don't have or wish to install 
papaja and its many dependencies. 
JB: Yes, that's a good note to include for folks.
-->

<!-- The .bib file is now just from our shared library -->

```{r setup, include = FALSE}
library(papaja) #install with devtools1
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros & round_tidy
library(psych) #for correlation matrices
library(tidyselect) 
#library(psychometric) # for correlation confidence intervals - might not need...
library(broom)

@@

#The ordering of this table also doesn't match the one above, which I'm leaving for the moment since we probably want to set
#an order of items/norms and stick to it consistently throughout

@@

<!-- do the histograms change our interpretation here? -->

@@

<!-- ## Directions for future research

MW: Do we need directions.. or just leave out to conserve word count?-->

@@

<!-- MW: I've added this subsection because it's signalled as a required heading in the abstract. Is there more to say here?-->

@@

practice_labels <- c(
  available_data = "Data on\nrequest",
  detailed_methodology = "Info\nrequired\nfor replication",
  harking = "HARKing",
  incomplete_results = "p-hacking",
  open_access = "Open access",
  registered_reports = "Registered reports",
  open_data = "Open data",
  open_materials = "Open\nmaterials",
  preprint_pre = "Preprints",
  preregistration = "Preregistration",
  registered_report = "Registered\nreport"
)

@@

#[breadcrumb: need to update the theme]

@@

We used `r cite_r("r-references.bib")` for all our analyses.

<!-- This is nice to do, but it generate a 150+ word paragraph of citations to packages, including citations to packages our code doesn't directly use (e.g. nlme, multilevel, etc.). We might need to cut it down manually to a more concise list?

EK: You can edit the r-refs bib directly to remove the packages that are just dependencies
-->

>>>>

---
title: What do incoming university students believe about open science practices in
  psychology?
author:
  - name: Jennifer L. Beaudry
    affiliation: '1,4'
    role:
      - Conceptualization
      - Data curation
      - Formal analysis
      - Investigation
      - Methodology
      - Project administration
      - Validation
      - Visualization
      - Writing - original draft
      - Writing - review & editing
    corresponding: yes
    email: jen.beaudry@flinders.edu.au
    address: Enter postal address here
  - name: Matt N. Williams
    affiliation: '2'
    role:
      - Investigation
      - Methodology
      - Validation
      - Writing - original draft
    email: m.n.williams@massey.ac.nz
  - name: Michael C. Philipp
    affiliation: '2'
    role:
      - Conceptualization
      - Investigation
      - Methodology
      - Project administration
      - Writing - original draft
    email: m.philipp@massey.ac.nz
  - name: Emily J. Kothe
    affiliation: '3'
    role:
      - Conceptualization
      - Data curation
      - Validation
      - Visualization
      - Writing - review & editing
    email: emily.kothe@deakin.edu.au

affiliation:
  - id: '1'
    institution: Flinders University
  - id: '2'
    institution: Massey University, New Zealand
  - id: '3'
    institution: Deakin University
  - id: '4'
    institution: Swinburne University of Technology

shorttitle: Psychology students' beliefs about open science
output:
  papaja::apa6_word: default
  papaja::apa6_pdf: default
abstract: |
 BACKGROUND: Understanding students’ naive conceptions about how science works and the norms that guide scientific best practice is important so that teachers can adapt their teaching to the students’ existing understandings.
 OBJECTIVE: To describe what incoming undergraduate students of psychology believe about reproducibility and open science practices in spsychology.
 METHOD: International online survey with participants who were about to start their first course in psychology at a university (N = 239) .
 RESULTS: When asked about how research *should* be done, most students endorsed most (but not all) of ten open science practices. When asked to estimate the proportion of published psychological studies that apply each of a set of 10 open science practices, participants' estimates tended to average near 50%. Only 18% of participants had heard of the term "replication crisis".
 CONCLUSION: Despite relatively significant media attention on the replication crisis, few incoming psychology students are familiar with the term. Incoming students nevertheless appear to be sympathetic toward most open science practices, although they may overestimate the prevalence of these practices in psychology.
 TEACHING IMPLICATIONS: Teaching materials aimed at incoming psychology students should not assume pre-existing knowledge about open science or replicability.

keywords: open science, psychology, teaching, reproducibility, replication
wordcount:  3161 (need to update)
bibliography: ['r-references.bib','Undergrads & Open Science (public).bib']
floatsintext: yes
figurelist: no
tablelist: no
footnotelist: no
linenumbers: yes
mask: no
draft: no
documentclass: apa6
classoption: man
editor_options: 
  chunk_output_type: console
csl: "apa.csl" 
---

@@

<!-- To knit to RMarkdown you will probably need the papaja package installed, and to knit to .pdf you will need a tex distro (e.g., TinyTex). However, it is possible to run all the R code (without knitting to .docx or .pdf) by clicking Run > Run All Chunks Below. This could be useful in future for readers interested in reproducing results but who don't have or wish to install papaja and its many dependencies. -->

```{r setup, include = FALSE}
library(papaja) #install with devtools1
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros & round_tidy
library(tidyselect) 
library(broom)

@@

@@

@@

@@

@@

practice_labels <- c(
  available_data = "Data on\nrequest",
  detailed_methodology = "Information\nfor replication",
  harking = "HARKing",
  incomplete_results = "p-hacking",
  open_access = "Open access",
  registered_reports = "Registered reports",
  open_data = "Open data",
  open_materials = "Open\nmaterials",
  preprint_pre = "Preprints",
  preregistration = "Preregistration",
  registered_report = "Registered\nreport"
)

@@

@@

We used `r cite_r(file = "r-references.bib", pkgs = c("broom", "finalfit", "gendercoder", "here", "papaja", "tidyverse"), withhold = FALSE)` for our analyses.
